%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://www.thenewface.io/}{\underline{Immersive E-commerce Experiences}}} % Project title
    {Generalist Programmer} % Position
    {The New Face} % Organization, Location
    {Jul 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Resolved various \textbf{multiplayer-related bugs} caused by \textbf{race conditions}.}
        \item {Addressed \textbf{matchmaking issues} that resulted from design flaws, ensuring players could successfully matchmake.}
        \item {Updated the \textbf{GeForce Now SDK} to the latest version and fixed the \textbf{inbound messaging feature}, enabling clients to send messages to the GFN application.}
        \item {Optimized the \textbf{action zones feature} for mobile devices, ensuring the virtual keyboard displays when focusing on an editable text box in GeForce Now.}
        \item {Provided support for extra features that come with the GeForce Now SDK, and were not previously implemented.}
        \item {Customized the \textbf{Common Loading Screen plugin}, originally from Lyra, to control the \textbf{Movie Player} according to our needs.}
        \item {Automated the \textbf{integration process} of the GeForce Now SDK into our packaged builds, eliminating the need for manual intervention.}
        \item {Adapted quickly to the \textbf{GeForce Developer Portal} and utilized \textbf{debug seats} to troubleshoot our experiences on the GFN platform.}
        \item {Enhanced \textbf{testing inclusivity} by fine-tuning the client's GeForce Now SDK.}
        \item {Refactored parts of our core \textbf{codebase} to improve \textbf{maintainability} and \textbf{scalability}.}
        \item {Provided consultation on \textbf{design-related matters} for implementing new systems.}
        \item {Upgraded the \textbf{engine} and associated \textbf{plugins} to the latest versions, ensuring compatibility with the GeForce Now SDK.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://wizardcell.com/about/lords-of-the-fallen}{\underline{Lords of The Fallen}}} % Project title with hyperlink and underline
    {Junior Network Programmer} % Position
    {HEXWORKS - CI Games} % Organization, Location
    {Dec 2022 - Jun 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Made the game work from the \textbf{networking perspective}, while dealing with numerous aspects of the game that include but are not limited to:
          \begin{itemize}
            \item {\textbf{Matchmaking:}
              \begin{itemize}
                \item {Revamped our \textbf{Invasion Matchmaking System} while utilizing \textbf{Online Beacons}.}
                \item {Provisioned a \textbf{Custom Matchmaking by Key System}.}
                \item {Fixed our \textbf{Ping Calculation System}, ensuring clients are matchmade with good ping to the server.}
              \end{itemize}
            }
            \item {\textbf{Customization System:} Synchronized character customizations by \textbf{custom serialization \& compression} of data over the network to achieve atomic replication of data types unsupported by the Replication System.}
            \item {\textbf{Save/Serialization System:} Fixed vague game breaking issues that were caused by improper serialization of game state.}
            \item {\textbf{Gameplay Ability System:} Fixed several gameplay abilities not performing properly over the network, and made a few.}
            \item {\textbf{Character Movement \& Animation:} Various Game \& Engine level fixes to enhance the way characters move and animate.}
            \item {\textbf{Level Streaming:} Various Game \& Engine level fixes to ensure game state is synchronized and resilient against level streaming under harsh network conditions.}
            \item {\textbf{Level Design:} Implemented level design oriented tools to \textbf{enhance the workflow} of the level design team.}
            \item {\textbf{Audio:} Fixed countless audio bugs, where audio wasn't played properly across the network for all connections of interest.}
            \item {\textbf{UI:}
              \begin{itemize}
                \item {Fixed visually breaking issues with different in-game menus, and handled a bunch of memory leaks.}
                \item {Provisioned a dedicated, self-contained \textbf{multiplayer settings menu}.}
                \item {Provisioned \textbf{user-facing text localization}.}
              \end{itemize}
            }
          \end{itemize}
        }
        \item {Profiling and optimizing game's \textbf{network bandwidth} using \textbf{Networking Insights:}
        \begin{itemize}
          \item {Effectively identified and disabled replication on many Objects and properties that didn't need it.}
          \item {Effectively skipped data replication for connections that were able to conclude that data from elsewhere.}
          \item {Utilized \textbf{Oodle Network} plugin to manually compress serialized network data for improved player experience.}
          \item {Seamlessly moved bandwidth-unfriendly data to Objects that replicate less frequently, and persist longer.}
        \end{itemize}
        }
        \item {Profiling and optimizing game's \textbf{server CPU performance} usage using \textbf{Timing Insights}.}
        \item {Provisioned editor tools, that simplified and enhanced my workflow:
        \begin{itemize}
          \item {Made a simple editor tool that scans all our project's Blueprint assets, and inclusively finds potentially optimizable replicating Objects.}
          \item {Made a simple editor tool that triggers serialization on Blueprint assets, so that references to Gameplay Attributes can be seen in the reference viewer, to better understand how to optimize their owning Attribute Sets.}
        \end{itemize}
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://wizardcell.com/about/bulletville}{\underline{BulletVille}}} % Project title
    {Junior Programmer} % Position
    {NOWWA} % Organization, Location
    {Jan 2022 - May 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a \textbf{game-mode based Spectating System}.}
        \item {Implemented \textbf{Killcam System} for instant replays.}
        \item {Collaborated with the design team to implement and refine game features based on playtesting and user feedback.}
        \item {Contributed to building the project's \textbf{Style Guide} and helped organizing its hierarchy.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://wizardcell.com/about/anarea}{\underline{Anarea Battle Royale}}} % Project title
    {Novice Gameplay Programmer} % Position
    {AXC Games} % Organization, Location
    {Jul 2019 - Aug 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented \textbf{Multizone Spawn System} inspired by the one in Ring of Elysium.}
        \item {Implemented \textbf{Loot Randomizer System}.}
        \item {Developed an \textbf{Inventory System} to manage player items and equipment.}
        \item {Created and optimized various \textbf{gameplay mechanics}, including player movement, shooting, and health systems.}
        \item {Integrated third-party \textbf{APIs} for analytics and player feedback.}
        \item {Collaborated with the \textbf{design team} to implement and refine game features based on playtesting and user feedback.}
        \item {Worked on \textbf{network synchronization} to ensure smooth multiplayer gameplay.}
        \item {Assisted in \textbf{debugging} and resolving performance issues to enhance game stability and performance.}
        \item {Participated in \textbf{code reviews} and provided constructive feedback to improve code quality and maintainability.}
        \item {Contributed to the development of the game's \textbf{user interface}, including HUD elements and menus.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
