%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}

%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/WizardCell/Yalla-Negev}{\underline{Yalla Negev}}} % Project title
    {Android Application} % Project type
    {Technion, Haifa, Israel} % Institution, Location
    {Summer 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed a mobile application to collect and visualize reliable data regarding service availability in the Negev region.}
        \item {Implemented core backend services including \textbf{user authentication}, secure \textbf{data submission}, and real-time push notifications.}
        \item {Architected a \textbf{Firebase/Firestore database} to handle asynchronous client-server data synchronization.}
        \item {Iterated on application UI and UX based on extensive user playtesting and feedback collection.}
        \item {Project officially accepted for presentation at \textbf{IEEE} (2025).}
        \item {\textbf{Technologies:} Flutter, Dart, TypeScript, Firebase \& Firestore.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/WizardCell/Personal-Tracking-Board}{\underline{Personal Tracking Board}}} % Project title
    {Internet of Things (IoT) Project} % Project type
    {Technion, Haifa, Israel} % Institution, Location
    {Winter 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Engineered a C-based IoT tracking system to monitor and visualize user-specific task progression in real-time.}
        \item {Implemented \textbf{NTP clock synchronization} to ensure precise state consistency and accurate timekeeping across the hardware.}
        \item {Engineered network logic handling HTTP requests to a Firestore backend for reliable \textbf{data synchronization}.}
        \item {Utilized \textbf{multithreading} on the ESP32 to offload asynchronous network requests to a background thread, preventing UI blocking and ensuring a smooth display framerate.}
        \item {\textbf{Technologies:} C, ESP32, Arduino, HTTP \& NTP Protocols.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}