%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/WizardCell/Yalla-Negev}{\underline{Yalla Negev}}} % Project title
    {Android Application} % Project type
    {Technion, Haifa, Israel} % Institution, Location
    {Summer 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed an Android application that aims to collect reliable data about service availability in the Negev region to advocate for government support.}
        \item {Implemented key features such as user registration/authentication, data submission, and push notifications.}
        \item {Set up the Firebase/Firestore database to enable seamless communication between the app and the backend.}
        \item {Designed a user-friendly interface for data collection and visualization.}
        \item {Conducted user testing and feedback collection to improve application usability.}
        \item {Technologies: Flutter, Dart, TypeScript, Firebase \& Firestore.}
        \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {\href{https://github.com/WizardCell/Personal-Tracking-Board}{\underline{Personal Tracking Board}}} % Project title
    {Internet of Things Project} % Project type
    {Technion, Haifa, Israel} % Institution, Location
    {Winter 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) bullet points
        \item {Developed an IoT-based personal tracking board that helps track the progress of user-created assignments per board user.}
        \item {Implemented NTP clock synchronization to ensure accurate timekeeping across the board.}
        \item {Handled HTTP requests to the Firestore database to synchronize data and display accurate assignment status on the board.}
        \item {Utilized multithreading on the ESP32 to perform HTTP requests on a separate thread, ensuring the display of the board never hangs.}
        \item {Technologies: C, ESP32, Arduino, HTTP \& NTP Protocols.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}